---
title: DANL Project-Beer Analytics
subtitle: "Data-Driven Mastery: Unlocking Business Potential"
author: 
  - Jake Marcell
  - Sophia Rodger
  - McAndrew Bean
  - Jacob Knapp
  - Blaise Leone

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)
library(ggplot2)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Introduction

Welcome to the exploration of alcohol trends in popular beer brands! In this project, we delve into a data set containing information on different beer brands. Our focus is on understanding the relationship that age has among buying these brands, providing insights into the diverse world of beers. :beers: :clap:

# Data

The data set 'beer_data' contains a curated selection of beer brands. Let's begin by exploring the summary statistics to gain an initial understanding of the data set. :beers:

## Summary Statistics

```{r}
beer_data <- read_csv('https://bcdanl.github.io/data/beer_markets.csv') 
```


The 'skim' function is used to generate summary statistics, providing key insights into central tendencies, dispersions, and other relevant characteristics of the dataset. The 'select(-n_missing)' part excludes information about missing values.
```{r}
skim(beer_data) %>% 
  select(-n_missing)

# The summary statistics provide us with key insights into the central 
# tendencies, dispersions, and other relevant characteristics of the dataset.
```


# Top 5 Beer Brands by Age Group
The code below calculates summary statistics (mean, median, max, min) of total beer volume by brand for each age group. The results are then arranged to identify the top 5 beer brands in terms of total volume for each age group.
```{r}
age_brand_preference <- beer_data %>%
  group_by(age, brand) %>%
  summarize(total_floz = sum(beer_floz)) %>%
  arrange(age, desc(total_floz)) %>%
  group_by(age) %>%
  slice(1:5)
age_brand_preference
```


# Visualization: Top 5 Beer Brands by Age Group
The following code utilizes the ggplot2 library to create a bar chart visualizing the top 5 beer brands for each age group based on total beer volume.
```{r}
library(ggplot2)

ggplot(age_brand_preference, aes(x = age, y = total_floz, fill = brand)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Top 5 Beer Brands by Age Group",
       x = "Age Group",
       y = "Total Beer Volume (floz)",
       fill = "Brand") +
  theme_minimal()

```

# Transaction Counts per Brand for Age Groups
The next code segment calculates the number of transactions for each beer brand within different age groups. The results are then visualized using a scatter plot with facets for each brand.
```{r}

beer_data$brand <- as.factor(beer_data$brand)
beer_data$age <- as.factor(beer_data$age)

transaction_counts <- beer_data %>%
  group_by(age, brand) %>%
  summarise(TransactionCount = n())


ggplot(transaction_counts, aes(x = age, y = TransactionCount)) +
  geom_point() +
  facet_wrap(~brand, scales = "free_y") +
  labs(title = "Number of Transactions per Brand for Age",
       x = "Age",
       y = "Transaction Count")

```

# Conclusion

These visualizations and analyses offer insights into consumer preferences for beer brands across different age groups, shedding light on which brands are most popular in terms of both total volume and transaction counts.


