---
title: DANL Project-Beer Analytics
subtitle: "Data-Driven Mastery: Unlocking Business Potential"
author: 
  - Jake Marcell
  - Sophia Rodger
  - McAndrew Bean
  - Jacob Knapp
  - Blaise Leone

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)
library(ggplot2)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Introduction

Welcome to the exploration of alcohol trends in popular beer brands! In this project, we delve into a data set containing information on different beer brands. Our focus is on understanding the relationship that age has among buying these brands, providing insights into the diverse world of beers. :beers: :clap:

# Data

The data set 'beer_data' contains a curated selection of beer brands. Let's begin by exploring the summary statistics to gain an initial understanding of the data set. :beers:

## Summary Statistics

```{r}
beer_data <- read_csv('https://bcdanl.github.io/data/beer_markets.csv') 
```

```{r}
skim(beer_data) %>% 
  select(-n_missing)

# The summary statistics provide us with key insights into the central 
# tendencies, dispersions, and other relevant characteristics of the dataset.
```

```{r}
age_brand_preference <- beer_data %>%
  group_by(age, brand) %>%
  summarize(total_floz = sum(beer_floz)) %>%
  arrange(age, desc(total_floz)) %>%
  group_by(age) %>%
  slice(1:5)
age_brand_preference
# This code calculates summary statistics (mean, median, max, min) 
# of total beer volume by brand for each age group.
```

```{r}
library(ggplot2)

ggplot(age_brand_preference, aes(x = age, y = total_floz, fill = brand)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Top 5 Beer Brands by Age Group",
       x = "Age Group",
       y = "Total Beer Volume (floz)",
       fill = "Brand") +
  theme_minimal()

```


```{r}

beer_data$brand <- as.factor(beer_data$brand)
beer_data$age <- as.factor(beer_data$age)

transaction_counts <- beer_data %>%
  group_by(age, brand) %>%
  summarise(TransactionCount = n())


ggplot(transaction_counts, aes(x = age, y = TransactionCount)) +
  geom_point() +
  facet_wrap(~brand, scales = "free_y") +
  labs(title = "Number of Transactions per Brand for Age",
       x = "Age",
       y = "Transaction Count")

```

